The binary liquid model for gravity-driven microchannel simulations

### 2010-10-22 Text/paper.tex
Added results for the wall gradient. Need to add some numbers.

Here are two different examples presented that can quantitatively show the
initialization procedure for quite different capillary numbers. In these
examples we use $k=0.04$ and $A=0.04$ as optimal binary liquid model parameters.
That explicitly implies the surface tension to be $\sqrt{\frac{8 k
A}{9}}=0.0377$ and the characteristic length of the interface
$5\sqrt{\frac{k}{A}}=5$ lattice boltzmann units. For the sake of simplicity and
stability the relaxations parameter for liquid and gas phases are taken as
$\tau_{liq}=2.5$ and $\tau_{gas}=0.7$. That gives the gas-liquid viscosity ratio
as $10$.  
\begin{description}
 \item[I \bm{$Ca=0.005$}]
  The film width for such small Capillary numbers \cite{bretherton} is
given by equation:
  \begin{equation}
  \frac{h_{\infty}}{H}=1.3375 Ca^{2/3}=0.03899,
  \end{equation}
  where we assume that $2 H$ or $Ny$ in lattice units is the channel width.
Therefore one needs to resolve the interface which is around $2$ percent of
  whole channel width with for instance $8$ lattice units, where $5$ lattice
units occupies the interface width for given. Note that the interface occupies
$62.5$ percent of the interface.  Therefore the channel
  width is $400$ lattice units. We take the bubble length as $5$ channel widths
  and the distance between bubble is as $2$ bubble lengths. It gives the
grid size as $400\mathrm{x}6000$. In terms of computer memory
requirement the calculations with the double precision accuracy demand:
\begin{equation}
\begin{aligned}
&2\text{ set of populations }\mathrm{x}\,\, 8\,\, \text{bytes per population
}\mathrm{x}\,\, 9 \text{ number of
populations}\\
&\mathrm{x}\,400\,\mathrm{x}\,6000\approx 345 \mathrm{MB}. 
\end{aligned}
\end{equation}
Even with this naive assumption for the $50$ percent resolution of the film
widht in comparison with the interface width, one can get the memory
requirement as $345 MB$.

@@

\subsection{The influence of the wall gradient}
Once the procedure of how to resolve the interface gradient is known, we want
to examine the influence of the phase gradient, i.e. the wettability of the
wall, to the film thickness. We examined the
wall gradient influence on
the standard grid $202\mathrm{x}3001$ and the initial film width as
{\color{red} Take the value from previous calculations $20$}
lattice boltzmann units. We examined $11$ different values for the wall
gradient ranging from $-1$ to $1$. The results are consistent among all the
wall gradients given that the interface is resolved in the right way. For the
given wall gradients the values of interface thicknesses are
{\color{red} Change these numbers $0.0709130255276, 0.0708903443305,
0.0708661222722,
0.0708369188112, 0.0707962325316, 0.0707266326981, 0.0705839443249,
0.0702489349415, 0.0697553433989$}. For the wall gradients $0.8$ and $1.0$ the
values are NAN. The negative values of the phase gradient are preferable, as
far as the phase of the liquid adjacent to the wall has the value of $1$. That
means that the phase values near the wall are above $1$. In case of positive
gradients the values near the wall are below $1$ and the gradient profile can
fuse with the values of the gas phase as $-1$, creating the wall stickyness,
unphysical one. {\color{red} Michal, if you want to add some pictures go ahead
with it}.

\section{The influence of different viscosities}
The results obtained earlier are taken for the liquiqs viscosity ratio $10$.
We performed the same simulations for the liquids viscosity ratio as $20$.
Parameters were taken as $\tau_{liquid}=4.5$ and $\tau_{bubble}=0.7$. 
{\color{red} The results showed that blah-blah-blah - I guess will be the same}.

>>>>

Here two different examples are presented that can quantitatively show the
initialization procedure for quite different capillary numbers. In these
examples we use $k=0.04$ and $A=0.04$ as optimal binary liquid model parameters.
That explicitly implies the surface tension to be $\sqrt{\frac{8 k
A}{9}}=0.0377$ and the characteristic length of the interface
$5\sqrt{\frac{k}{A}}=5$ lattice boltzmann units. For the sake of simplicity and
stability the relaxations parameter for liquid and gas phases are taken as
$\tau_{liq}=2.5$ and $\tau_{gas}=0.7$. That gives the gas-liquid viscosity ratio
as $10$.  
\begin{description}
 \item[I \bm{$Ca=0.005$}]
  The film width for such small Capillary numbers \cite{bretherton} is
given by equation:
  \begin{equation}
  \frac{h_{\infty}}{H}=1.3375 Ca^{2/3}=0.03899,
  \end{equation}
  where we assume that $2 H$ or $Ny$ in lattice units is the channel width.
Therefore one needs to resolve the interface which is around $2$ percent of
  whole channel width with for instance $8$ lattice units, where $5$ lattice
units occupies the interface width for given. Note that the interface occupies
$62.5$ percent of the interface.  Therefore the channel
  width is $400$ lattice units. We take the bubble length as $5$ channel widths
  and the distance between bubble is as $2$ bubble lengths. It gives the
grid size as $400\mathrm{x}6000$. In terms of computer memory
requirement the calculations with the double precision accuracy demand:
\begin{equation}
\begin{aligned}
&2\text{ set of populations }\mathrm{x}\,\, 8\,\, \text{bytes per population
}\mathrm{x}\,\, 9 \text{ number of
populations}\\
&\mathrm{x}\,400\,\mathrm{x}\,6000\approx 345 \mathrm{MB}. 
\end{aligned}
\end{equation}
Even with this naive assumption for the $50$ percent resolution of the film
widht in comparison with the interface width, one can get the memory
requirement as $345 MB$.

@@

\subsection{The influence of the wall gradient}
The results should not depend on the wall wettability. Wettability is defined
through the phase gradient \cite{pooley-contact}, $\partial_n \phi$. This
section is to examine the wall gradient influence on simulations. We take large
enough resolution for simulations to be consistent. Simulation domain was
chosen as $177\mathrm{x}2626$ and the initial film width as
$12$ lattice boltzmann units, which correspond to the predicted film thickness.
We examined $11$ different values for the wall
gradient ranging from $-1$ to $1$. The results are consistent among all the
wall gradients given that the interface is resolved in the right way. For the
given wall gradients the values of interface thicknesses are
{\color{red} Change these numbers $0.0709130255276, 0.0708903443305,
0.0708661222722,
0.0708369188112, 0.0707962325316, 0.0707266326981, 0.0705839443249,
0.0702489349415, 0.0697553433989$}. For the wall gradients $0.8$ and $1.0$ the
simulations are unstable. One can see the simulated profiles in Fig.
\ref{fig:gradients:profiles} The negative values of the phase gradient are
preferable, as
far as the phase of the liquid adjacent to the wall has the value of $1$. That
means that the phase values near the wall are above $1$. In case of positive
gradients the values near the wall are below $1$ and the gradient profile can
fuse with the values of the gas phase as $-1$, creating the wall stickyness,
unphysical one. {\color{red} Michal, if you want to add some pictures go ahead
with it}.
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/Wall/phase_grad_profiles.eps}
\caption{Phase profiles for different wall gradients. One can see if the width
is properly resolved then the wettability of the wall doesn't play any role
affecting the film thickness.
\label{fig:gradients:profiles}
}
\end{figure}
\section{The influence of different viscosities}
The results obtained earlier are taken for the liquiqs viscosity ratio $10$.
We performed the same simulations for the liquids viscosity ratio as $20$.
Parameters were taken as $\tau_{liquid}=4.5$ and $\tau_{bubble}=0.7$. 
{\color{red} The results showed that blah-blah-blah - I guess will be the same}.
